Between-dataset comparisons

### 2019-11-14 analysis/reports/cross_dataset.Rmd
fix cross dataaset report

 all_di[[i]] <- readd(all_di, cache = cache)
 all_di[[i]] <- filter(all_di[[i]], source == "observed")

>>>>

  if("all_di" %in% cached(cache = cache)) {
    all_di[[i]] <- readd(all_di, cache = cache)
  } else {
    all_di_names <- cached(cache = cache)[ which(grepl(cached(cache = cache), pattern = "all_di_s_"))]
    all_di_list <- lapply(all_di_names, FUN = readd, cache = cache, character_only =T)
    names(all_di_list) <- all_di_names
    all_di[[i]] <- bind_rows(all_di_list)
    rm(all_di_names)
    rm(all_di_list)
  }
  all_di[[i]] <- filter(all_di[[i]], source == "observed")
